---
title: "parameter recovery"
author: "Kendra Seaman"
date: "3/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#knitr::opts_chunk$set(fig.width=5, fig.height=3.5) 
library(here)
source(here::here('17_model_param_recovery.R'))
```

For each set of graphs:
graph 1 - true value (sim) compared to estimated value (fit)
graph 2 - difference between true value (sim) and estimated value (fit) faceted by true value


### baseline model
#### beta
```{r baseline, echo = FALSE, message=FALSE, fig.show="hold", out.width="50%"}
bl_beta
bl_betadiff
```

### general learning model 
#### alpha
```{r general alpha, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a1_alpha
a1_alphadiff
```

#### beta
```{r general beta, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a1_beta
a1_betadiff
```

### general learning with decay  model 
#### alpha
```{r general decay alpha, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a1d_alpha
a1d_alphadiff
```

#### beta
```{r general decay beta, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a1d_beta
a1d_betadiff
```

#### decay
```{r general decay decay, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a1d_decay
a1d_decaydiff
```

### gain-loss learning model
#### alpha gain
```{r gain-loss alpha g, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2_alpha_gain
a2_diffAlphaGain
```

#### alpha loss
```{r gain-loss alpha l, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2_alpha_loss
a2_diffAlphaLoss
```

#### beta
```{r gain-loss beta, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2_beta
a2_diffBeta
```

### gain-loss learning with decay  model
#### alpha gain
```{r gain-loss decay ag, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2d_alpha_gain
a2d_diffAlphaGain
```

#### alpha loss
```{r gain-loss decay al, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2d_alpha_loss
a2d_diffAlphaLoss
```

#### beta 
```{r gain-loss decay beta, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2d_beta
a2d_diffBeta
```

#### decay
```{r gain-loss decay decay, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2d_decay
a2d_diffDecay
```

### gain-loss learning with priors model
#### alpha gain
```{r gain-loss prior ag, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2p_alpha_gain
a2p_diffAlphaGain
```

#### alpha loss
```{r gain-loss prior al, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2p_alpha_loss
a2p_diffAlphaLoss
```

#### beta
```{r gain-loss prior beta, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2p_beta
a2p_diffBeta
```

#### initial probs
```{r gain-loss prior iprobs, echo=FALSE, message=FALSE, fig.show="hold", out.width="50%"}
a2p_iprobA
a2p_diffIProbA
a2p_iprobB
a2p_diffIProbB
a2p_iprobC
a2p_diffIProbC
```